{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-11-05 documents/acknowledgement.tex
test

Thanks to (Dr. ) Barfuss for spending time reviewing an early draft.

@@

Prof. Griffiths and Dr. Brovko at UGuelph, Dr. Anany at the Guelph Research and Development Centre for tips on the Beta-Glo assay.

Thanks to L.H. for wisdom regarding this project; Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating ramblings.

@@

R.I.P. to Dr. Robert Adair, whose work features prominently here, died Sep. 2020.

@@

The authors reluctantly acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for going through the trouble to develop the AustinMan and AustinWoman human body models and then making them unavailable at https://sites.utexas.edu/austinmanaustinwomanmodels/, and also unavailable via email.

@@

The authors acknowledge the IT.IS foundation for doing precisely the same, but actually replying to emails.

@@

{\Large <3}

>>>>

Thanks to (Dr. ) P. Barfuss for spending time reviewing an early draft.

@@

Prof. Griffiths and Dr. Brovko at UGuelph, Dr. Anany at the GRDC for tips on the Beta-Glo assay

Professor Z-G Wang at Caltech for a note on electrostatics,

Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating ramblings.

Thanks to L.H. for wisdom regarding this project;

@@

R.I.P. to Dr. Robert Adair, whose work features prominently here, who died Sep. 2020.

@@

The authors reluctantly acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for going through the trouble to develop the AustinMan and AustinWoman human body models and then making them unavailable at https://sites.utexas.edu/austinmanaustinwomanmodels/, and also not replying to email.

It's okay, I'm not bitter.

@@

The authors gratefully acknowledge the IT.IS foundation for the same, and also compiling the tissue property databases.

@@

{\Large {\verbatim <3}}
